thesis2024

### 2025-05-07 02-creating-frames.qmd
Corrected \newpage locations and removed unused qmd

petrolist <- read_csv(here::here("data/02-creating-frames/petro_sample.csv"))
knitr::kable(petrolist) |> 
  kable_styling(latex_options = c("striped", "scale_down", "repeat_header"))

>>>>

petrolist <- read_csv(here::here("data/02-creating-frames/petro_sample.csv"))
knitr::kable(petrolist)
  #kable_styling(latex_options = c("striped", "scale_down", "repeat_header"))

### 2025-05-07 05-stone-to-tool.qmd
Corrected \newpage locations and removed unused qmd

The Solutrean assemblage technological analysis was published by Cascalheira [-@cascalheiraTecnologiaLiticaAbrigo2009] as part of a Master’s thesis and following publications [e.g., @cascalheiraValeBoiAlgarve2013 ;@cascalheiraTecnologiaLiticaSolutrense2010], with the study of levels A to C of the Shelter area. The dataset used for this study was not originally published but can be consulted in our online repository (<http://www.doi.org/10.17605/OSF.IO/UWMPK>).

@@

One challenge of integrating datasets collected by different researchers is variability in methodologies and recorded variables. However, this study minimizes such inconsistencies by ensuring methodological alignment across datasets, as all data collection followed standardised attribute-based lithic analysis protocols. The lithic analysis datasets used in this study adopted an attribute-based methodology, which aims to describe morphological and metrical attributes of technological classes. The attributes analysed followed those present in specialised literature, such as Brézillon @brezillonDenominationObjetsPierre1968 and @tixierPrehistoirePierreTaillee1980, paired with other Palaeolithic lithic attribute analyses \[e.g., @bichoTechnologicalChangeFinal1992; @zilhaoPaleoliticoSuperiorEstremadura1997; @cascalheiraTerritorialityOrganizationTechnology2019; @tostevinSeeingLithicsMiddlerange2012\].

>>>>

The Solutrean assemblage technological analysis was published by Cascalheira [-@cascalheiraTecnologiaLiticaAbrigo2009] as part of a Master’s thesis and following publications [e.g., @cascalheiraValeBoiAlgarve2013; @cascalheiraTecnologiaLiticaSolutrense2010], with the study of levels A to C of the Shelter area. The dataset used for this study was not originally published but can be consulted in our online repository (<http://www.doi.org/10.17605/OSF.IO/UWMPK>).

@@

One challenge of integrating datasets collected by different researchers is variability in methodologies and recorded variables. However, this study minimizes such inconsistencies by ensuring methodological alignment across datasets, as all data collection followed standardised attribute-based lithic analysis protocols. The lithic analysis datasets used in this study adopted an attribute-based methodology, which aims to describe morphological and metrical attributes of technological classes. The attributes analysed followed those present in specialised literature, such as Brézillon @brezillonDenominationObjetsPierre1968 and @tixierPrehistoirePierreTaillee1980, paired with other Palaeolithic lithic attribute analyses [e.g., @bichoTechnologicalChangeFinal1992; @zilhaoPaleoliticoSuperiorEstremadura1997; @cascalheiraTerritorialityOrganizationTechnology2019; @tostevinSeeingLithicsMiddlerange2012].
